rbf.qmd

### 2023-06-12 Visuals_Interactives/mermaid_consort.qmd
tikz plots and slight reorganization.

>>>>

```{dot}
digraph ALM {
    rankdir = LR
    splines=false // straight lines, not curves

    // define input nodes
    Input1 [label="Input1"]
    Input2 [label="Input2"]

    // define output nodes
    Output1 [label="Output1"]
    Output2 [label="Output2"]
    Output3 [label="Output3"]

    // define equations
    equation1 [shape=none, label="a_i(X) = e^{-γ(X-X_i)^2}, normalized: a_i(X) / Σa_i(X)", fontsize=10]
    equation2 [shape=none, label="O_j(X) = Σ w_{ji} ⋅ a_i(X), P[Y_j | X] = O_j(X) / Σ O_k(X)", fontsize=10]

    // define invisible nodes for alignment
    invis1 [style=invis]
    invis2 [style=invis]

    // edges between input nodes and output nodes
    Input1 -> Output1 [label="w_{11}"]
    Input1 -> Output2 [label="w_{12}"]
    Input1 -> Output3 [label="w_{13}"]

    Input2 -> Output1 [label="w_{21}"]
    Input2 -> Output2 [label="w_{22}"]
    Input2 -> Output3 [label="w_{23}"]

    // align input nodes and equations on same rank
    {rank=same Input1 Input2 equation1 invis1}
    {rank=same Output1 Output2 Output3 equation2 invis2}

    // invisible edges to order nodes
    edge [style=invis]
    Input1 -> Input2 -> equation1 -> invis1
    Output1 -> Output2 -> Output3 -> equation2 -> invis2
}

```{dot}
digraph ALM {
    rankdir = LR
    splines=false // straight lines, not curves

    // Define input layer with rectangle
    subgraph cluster_input {
        label="Input Layer";
        style=filled;
        color=lightgrey;
        Input1 [label="Input1"]
        Input2 [label="Input2"]
    }

    // Define output layer with rectangle
    subgraph cluster_output {
        label="Output Layer";
        style=filled;
        color=lightgrey;
        Output1 [label="Output1"]
        Output2 [label="Output2"]
        Output3 [label="Output3"]
    }

    // Define equations (using simplified text as Graphviz has limited text formatting options)
    equation1 [shape=plaintext, label="Input activation ai(X) = exp(-gamma*(X-Xi)^2), normalized by dividing by sum", fontsize=10]
    equation2 [shape=plaintext, label="Output Oj(X) = sum(w_ji * ai(X)), Probability P[Yj | X] = Oj(X) / sum(Ok(X))", fontsize=10]

    // Edges between input nodes and output nodes
    Input1 -> Output1 [label="w_11"]
    Input1 -> Output2 [label="w_12"]
    Input1 -> Output3 [label="w_13"]

    Input2 -> Output1 [label="w_21"]
    Input2 -> Output2 [label="w_22"]
    Input2 -> Output3 [label="w_23"]

    // Invisible nodes for alignment
    invis1 [style=invis]
    invis2 [style=invis]

    // Align input nodes and equations on same rank
    {rank=same equation1 invis1}
    {rank=same equation2 invis2}

    // Invisible edges for ordering
    edge [style=invis]
    equation1 -> invis1
    equation2 -> invis2
}

```{dot}

digraph G {
rankdir = LR
splines=false  // straight lines, not curves
// define ellipsis nodes
E1[shape=none  label="&#8942;" fontsize=30]
E2[shape=none  label="&#8942;" fontsize=30]
{rank=same a b E1 z}       // align on same rank
{rank=same x1 x2 E2 x100}  // align on same rank

{a b z} -> {x1, x2, x100} -> Y

// invisible edges to order nodes
edge[style=invis]
a->b->E1->z 
x1->x2->E2->x100 
}

```{dot}
digraph G {
 graph [rankdir=LR]
 node [shape=none label=""]
 node [imagescale=true]
 n1  [ image="Visuals_Interactives/pic1.svg" ]
 n2  [ image="image_dir/longeqns2.png" ]
 n3  [ image="image_dir/Eggequation.jpg" ]
 n4  [ shape=rect image="image_dir/LaTeX-arrow.png" ]
 n5  [ shape=circle image="image_dir/main-qimg.png"]
 n6  [ shape=rect image="image_dir/LaTeX-arrow.png" ]

 n1 -> { n2 n3}
 n2-> n4 -> n5 -> n6

subgraph clusterX {
 node [imagescale=true]
 J1  [ image="image_dir/LaTeX-arrow.png" ]
 J2  [ shape=rect image="image_dir/longeqns2.png" ]
 J4  [ image="image_dir/LaTeX-arrow.png" ]
 J5  [ shape=rect image="image_dir/main-qimg.png"]
 J6  [ shape=circle image="image_dir/LaTeX-arrow.png" ]
}
 J1 -> J2
 J1-> J6 -> J5 -> J4
}

```{dot}

digraph G {
rankdir = LR
splines=false  // straight lines, not curves
// define ellipsis nodes
E1[image="Visuals_Interactives/gaussian_curve_input_node_1.png"]
E2[shape=none  label="&#8942;" fontsize=30]
{rank=same a b E1 z}       // align on same rank
{rank=same x1 x2 E2 x100}  // align on same rank

{a b z} -> {x1, x2, x100} -> Y

// invisible edges to order nodes
edge[style=invis]
a->b->E1->z 
x1->x2->E2->x100 
}

```{dot}

digraph G {
 graph [rankdir=LR]
 node [shape=none label=""]
 n1  [ image="images/svg1.svg" ]
 n2  [ image="images/acclaim.svg" ]
 n4  [ image="images/acm.svg" ]

 n1 -> n2 -> n4 
}

```{dot}
digraph ALM {
    rankdir = LR;
    splines=false;
    edge[style=invis];
    ranksep= 1.4;

    {
        node [shape=circle, color=chartreuse, style=filled, fillcolor=chartreuse];
        Input1 [label=<X<sub>1</sub>>];
        Input2 [label=<X<sub>2</sub>>];
    }

    {
        node [shape=circle, color=coral1, style=filled, fillcolor=coral1];
        Output1 [label=<Y<sub>1</sub>>];
        Output2 [label=<Y<sub>2</sub>>]; 
        Output3 [label=<Y<sub>3</sub>>];
    }

    {
        rank=same;
        Input1 -> Input2 [style=invis];
    }

    {
        rank=same;
        Output1 -> Output2 -> Output3 [style=invis];
    }

    label_input [shape=plaintext, label="Input Layer"];
    label_input -> Input1;
    {rank=same; label_input; Input1};

    label_output [shape=plaintext, label="Output Layer"];
    label_output -> Output1;
    {rank=same; label_output; Output1};

    edge[style=solid, tailport=e, headport=w, labelangle=45, labeldistance=2.0];
    Input1 -> Output1 [label=<w<sub>11</sub>>];
    Input1 -> Output2 [label=<w<sub>12</sub>>];
    Input1 -> Output3 [label=<w<sub>13</sub>>];

    Input2 -> Output1 [label=<w<sub>21</sub>>];
    Input2 -> Output2 [label=<w<sub>22</sub>>];
    Input2 -> Output3 [label=<w<sub>23</sub>>];
}

```{dot}
digraph G {

    // ===============================
    // rankdir: directed graph drawn from left to right 
    // details: http://www.graphviz.org/doc/info/attrs.html
    // ===============================
    rankdir=LR;  
    edge[style=solid, tailport=e, headport=w];

    // ===============================
    // splines=line:  draw straight lines to connect nodes
    // ===============================
    splines=line;
    nodesep=".05";
    node [label=""];
    subgraph cluster_0 {
        color=white;
        label="layer 1 (input layer)";
        node [color=chartreuse, 
              style=filled, 
              shape=circle];

       // ==============================
       // Below label text format specifies subscript and superscript in graphviz
       // ==============================
        x0 [color=yellow, 
            fillcolor=yellow, 
            label=<x<sub>0</sub>>];
        x1 [fillcolor=chartreuse, 
            label=<x<sub>1</sub>>];
        x2 [fillcolor=chartreuse, 
            label=<x<sub>2</sub>>];
        x3 [fillcolor=chartreuse, 
            label=<x<sub>3</sub>>];
    }

    subgraph cluster_1 {
        color=white;
        label="layer 2 (hidden layer)";
        node [color=dodgerblue, 
              style=filled, 
              shape=circle];
        a02 [color=yellow, 
             fillcolor=yellow, 
             label=<a<sub>0</sub><sup>(2)</sup>>];

       // ==============================
       // Below label text doesn't match with the node naming (i.e. a12 should have label "a12" instead of "a52")
       // This is a dirty trick that to keep the nodes in the same layer with label sorted 
       // (i.e. a12, followed by a22, followed by a32, followed by a42, followed by a52)
       // ==============================
        a12 [fillcolor=dodgerblue, 
             label=<a<sub>5</sub><sup>(2)</sup>>];
        a22 [fillcolor=dodgerblue, 
             label=<a<sub>1</sub><sup>(2)</sup>>];
        a32 [fillcolor=dodgerblue, 
             label=<a<sub>2</sub><sup>(2)</sup>>];
        a42 [fillcolor=dodgerblue, 
             label=<a<sub>3</sub><sup>(2)</sup>>];
        a52 [fillcolor=dodgerblue, 
             label=<a<sub>4</sub><sup>(2)</sup>>];
    }

    subgraph cluster_2 {
        color=white;
        label="layer 3 (hidden layer)";
        node [color=dodgerblue, 
              style=filled, 
              shape=circle];
        a03 [color=yellow, 
             fillcolor=yellow, 
             label=<a<sub>0</sub><sup>(3)</sup>>];
        a13 [fillcolor=dodgerblue, 
             label=<a<sub>3</sub><sup>(3)</sup>>];
        a23 [fillcolor=dodgerblue, 
             label=<a<sub>4</sub><sup>(3)</sup>>];
        a33 [fillcolor=dodgerblue, 
             label=<a<sub>5</sub><sup>(3)</sup>>];
        a43 [fillcolor=dodgerblue, 
             label=<a<sub>1</sub><sup>(3)</sup>>];
        a53 [fillcolor=dodgerblue, 
             label=<a<sub>2</sub><sup>(3)</sup>>];
    }

    subgraph cluster_3 {
        color=white;
        label="layer 4 (output layer)";
        node [color=coral1, 
              style=filled, 
              shape=circle];
        O1 [fillcolor=coral1, 
            label=<a<sub>1</sub><sup>(4)</sup>>];
        O2 [fillcolor=coral1, 
            label=<a<sub>2</sub><sup>(4)</sup>>];
        O3 [fillcolor=coral1, 
            label=<a<sub>3</sub><sup>(4)</sup>>];
        O4 [fillcolor=coral1, 
            label=<a<sub>4</sub><sup>(4)</sup>>];
    }

   // ===============================
   // This is the trick to enforce the bias node stays at the top of 
   // vertical array of nodes in each layer
   // style=invisible: makes the edge connection invisible
   // dir=none: hide the arrow 
   // ===============================
    x0 -> a02 [style=invisible, dir=none];
    x0 -> a12;
    x0 -> a22;
    x0 -> a32;
    x0 -> a42;
    x0 -> a52;
    x1 -> a12;
    x1 -> a22;
    x1 -> a32;
    x1 -> a42;
    x1 -> a52;
    x2 -> a12;
    x2 -> a22;
    x2 -> a32;
    x2 -> a42;
    x2 -> a52;
    x3 -> a12;
    x3 -> a22;
    x3 -> a32;
    x3 -> a42;
    x3 -> a52;
    a02 -> a03 [style=invisible, dir=none];
    a02 -> a13;
    a02 -> a23;
    a02 -> a33;
    a02 -> a43;
    a02 -> a53;
    a12 -> a13;
    a12 -> a23;
    a12 -> a33;
    a12 -> a43;
    a12 -> a53;
    a22 -> a13;
    a22 -> a23;
    a22 -> a33;
    a22 -> a43;
    a22 -> a53;
    a32 -> a13;
    a32 -> a23;
    a32 -> a33;
    a32 -> a43;
    a32 -> a53;
    a42 -> a13;
    a42 -> a23;
    a42 -> a33;
    a42 -> a43;
    a42 -> a53;
    a52 -> a13;
    a52 -> a23;
    a52 -> a33;
    a52 -> a43;
    a52 -> a53;
    a03 -> O1;
    a13 -> O1;
    a23 -> O1;
    a33 -> O1;
    a43 -> O1;
    a53 -> O1;
    a03 -> O2;
    a13 -> O2;
    a23 -> O2;
    a33 -> O2;
    a43 -> O2;
    a53 -> O2;
    a03 -> O3;
    a13 -> O3;
    a23 -> O3;
    a33 -> O3;
    a43 -> O3;
    a53 -> O3;
    a03 -> O4;
    a13 -> O4;
    a23 -> O4;
    a33 -> O4;
    a43 -> O4;
    a53 -> O4;
}

```{dot}
digraph G {

        rankdir=LR
	splines=line

        node [fixedsize=true, label=""];

        subgraph cluster_0 {
		color=white;
		node [style=solid,color=blue4, shape=circle];
		x1 x2 x3;
		label = "layer 1 (Input layer)";
	}

	subgraph cluster_1 {
		color=white;
		node [style=solid,color=red2, shape=circle];
		a12 a22 a32;
		label = "layer 2 (hidden layer)";
	}

	subgraph cluster_2 {
		color=white;
		node [style=solid,color=seagreen2, shape=circle];
		O;
		label="layer 3 (output layer)";
	}

        x1 -> a12;
        x1 -> a22;
        x1 -> a32;
        x2 -> a12;
        x2 -> a22;
        x2 -> a32;
        x3 -> a12;
        x3 -> a22;
        x3 -> a32;

        a12 -> O
        a22 -> O
        a32 -> O

}
```

```{dot}
digraph G {
    rankdir = LR;
    splines=false;
    edge[style=invis];
    ranksep= 1.4;
    {
    node [shape=circle, color=yellow, style=filled, fillcolor=yellow];
    x0 [label=<x<sub>0</sub>>]; 
    a02 [label=<a<sub>0</sub><sup>(2)</sup>>]; 
    a03 [label=<a<sub>0</sub><sup>(3)</sup>>];
    }
    {
    node [shape=circle, color=chartreuse, style=filled, fillcolor=chartreuse];
    x1 [label=<x<sub>1</sub>>];
    x2 [label=<x<sub>2</sub>>]; 
    x3 [label=<x<sub>3</sub>>];
}
{
    node [shape=circle, color=dodgerblue, style=filled, fillcolor=dodgerblue];
    a12 [label=<a<sub>1</sub><sup>(2)</sup>>];
    a22 [label=<a<sub>2</sub><sup>(2)</sup>>];
    a32 [label=<a<sub>3</sub><sup>(2)</sup>>];
    a42 [label=<a<sub>4</sub><sup>(2)</sup>>];
    a52 [label=<a<sub>5</sub><sup>(2)</sup>>];
    a13 [label=<a<sub>1</sub><sup>(3)</sup>>];
    a23 [label=<a<sub>2</sub><sup>(3)</sup>>];
    a33 [label=<a<sub>3</sub><sup>(3)</sup>>];
    a43 [label=<a<sub>4</sub><sup>(3)</sup>>];
    a53 [label=<a<sub>5</sub><sup>(3)</sup>>];
}
{
    node [shape=circle, color=coral1, style=filled, fillcolor=coral1];
    O1 [label=<a<sub>1</sub><sup>(4)</sup>>];
    O2 [label=<a<sub>2</sub><sup>(4)</sup>>]; 
    O3 [label=<a<sub>3</sub><sup>(4)</sup>>]; 
    O4 [label=<a<sub>4</sub><sup>(4)</sup>>];
}
    {
        rank=same;
        x0->x1->x2->x3;
    }
    {
        rank=same;
        a02->a12->a22->a32->a42->a52;
    }
    {
        rank=same;
        a03->a13->a23->a33->a43->a53;
    }
    {
        rank=same;
        O1->O2->O3->O4;
    }
    a02->a03;  // prevent tilting
    l0 [shape=plaintext, label="layer 1 (input layer)"];
    l0->x0;
    {rank=same; l0;x0};
    l1 [shape=plaintext, label="layer 2 (hidden layer)"];
    l1->a02;
    {rank=same; l1;a02};
    l2 [shape=plaintext, label="layer 3 (hidden layer)"];
    l2->a03;
    {rank=same; l2;a03};
    l3 [shape=plaintext, label="layer 4 (output layer)"];
    l3->O1;
    {rank=same; l3;O1};
    edge[style=solid, tailport=e, headport=w];
    {x0; x1; x2; x3} -> {a12;a22;a32;a42;a52};
    {a02;a12;a22;a32;a42;a52} -> {a13;a23;a33;a43;a53};
    {a03;a13;a23;a33;a43;a53} -> {O1,O2,O3,O4};
}
```

```{dot}
 digraph threevar {
      rankdir=LR;
      size="8,4";
      node [fontsize=14 shape=box];
      edge [fontsize=10];
      center=1;
      {rank=min k }
      {rank=same X1 X2 X3 }
      {rank=max z1 z2 z3 }
      z1 [shape=circle label="d1"];
      z2 [shape=circle label="d2"];
      z3 [shape=circle label="d3"];
      k [label="?" shape="ellipse"];
      k -> X1 [label="n@_{S}"];
      k -> X2 [label="&theta;@^{(h)}"];
      k -> X3 [label="?3"];
      z1 -> X1;
      z2 -> X2;
      z3 -> X3;
    }

```{r}
grViz('digraph threevar {
      rankdir=LR;
      size="8,4";
      node [fontsize=14 shape=box];
      edge [fontsize=10];
      center=1;
      {rank=min k }
      {rank=same X1 X2 X3 }
      {rank=max z1 z2 z3 }
      z1 [shape=circle label="d1"];
      z2 [shape=circle label="d2"];
      z3 [shape=circle label="d3"];
      k [label="?" shape="ellipse"];
      k -> X1 [label="n@_{S}"];
      k -> X2 [label="&theta;@^{(h)}"];
      k -> X3 [label="?3"];
      z1 -> X1;
      z2 -> X2;
      z3 -> X3;
    }
      ')

### 2023-06-12 Visuals_Interactives/model_viz.qmd
tikz plots and slight reorganization.

uml <- '@startuml

@@

@@

```{r fig.width=11, fig.height=12}
# Load the required libraries
library(ggplot2)
library(ggpp)
library(tidyverse)
library(patchwork)

@@

```{r}
# Load the required libraries
library(ggplot2)
library(ggpp)
library(patchwork)
library(tidyverse)

@@

# Load the required packages
library(ggplot2)
library(png)

>>>>

### plantuml visualizations
```{r}
uml <- '@startuml

@@

alm_model_with_equations <- '
@startuml

note right of (Input Layer)
  <math>a_i(X)=e^{-\\gamma \\cdot(X-X_i)^2}</math>
  <math>Normalized: \\frac{a_i(X)}{\\sum a_i(X)}</math>
end note

note right of (Output Layer)
  blank
end note

@enduml
'

# Pass the PlantUML code to plantuml function
alm_model_with_equations <- plantuml(alm_model_with_equations)
plot(x=alm_model_with_equations)
```

@@

library(tidyverse)
library(ggforce)

theme_set(theme_grey() +
            theme_void() +
            theme(plot.margin = margin(0, 5.5, 0, 5.5)))

# Parameters
input_x <- c(1, 2)
output_x <- c(1.5, 2.5, 3.5)
input_y <- 3
output_y <- 1
activation_levels <- c(0.2, 0.7, 0.5)

# Input Layer
input_layer <- tibble(x = input_x, y = rep(input_y, length(input_x)))

# Output Layer
output_layer <- tibble(x = output_x, y = rep(output_y, length(output_x)), activation = activation_levels)

# Gaussian Activation
gaussian_activation <- tibble(
  x = seq(from = 0, to = 3, by = 0.01),
  y = exp(-2 * (x - 1)^2) + 2.5,
  x2 = x,
  y2 = exp(-2 * (x - 2)^2) + 2.5
)

# Plot
p <- ggplot() +
  # Input nodes
  geom_point(data = input_layer, aes(x = x, y = y), size = 4, color = 'green') +
  annotate("text", x = input_x, y = rep(input_y, length(input_x)) + 0.3, label = c("Input #1", "Input #2")) +

  # Gaussian Activations
  geom_line(data = gaussian_activation, aes(x = x, y = y), color = 'blue') +
  geom_line(data = gaussian_activation, aes(x = x2, y = y2), color = 'blue') +

  # Connections
  geom_segment(data = expand.grid(input_x, output_x), aes(x = Var1, xend = Var2, y = input_y, yend = output_y), arrow = arrow(type = 'closed', length = unit(0.2, 'inches'))) +

  # Output nodes
  geom_point(data = output_layer, aes(x = x, y = y), size = 4, color = 'red') +
  geom_bar(data = output_layer, aes(x = x, y = activation), stat = 'identity', position = 'dodge', fill = 'red', alpha = 0.3, width = 0.3) +
  annotate("text", x = output_x, y = rep(output_y, length(output_x)) - 0.3, label = c("Output #1", "Output #2", "Output #3")) +

  # Equation annotations
  annotate("text", x = 0.5, y = input_y + 1, label = "1", parse = TRUE) +
  annotate("text", x = 1.5, y = output_y - 1, label = "2 ", parse = TRUE) +

  # Input stimulus and output response
  annotate("text", x = mean(input_x), y = input_y + 1.3, label = "Input Stimulus") +
  annotate("text", x = mean(output_x), y = output_y - 1.3, label = "Output Response") +

  # Coordinate limits and axis labels
  coord_cartesian(xlim = c(0, 4), ylim = c(-1, 5)) +
  labs(x = "", y = "") +
  theme_void()

# Show the plot
print(p)
```

library(ggplot2)
library(ggrepel)

neural_network_plot <- function(layers, layer_labels = NULL, node_labels = c('x', 'y')) {
data <- expand.grid(layer = seq_along(layers), node = 1:max(layers))
data <- data[data$node <= layers[data$layer], ]

links <- data.frame()
for (i in 1:(length(layers) - 1)) {
start <- subset(data, layer == i)
end <- subset(data, layer == i + 1)
links <- rbind(links, expand.grid(from = start$node, to = end$node, from_layer = start$layer, to_layer = end$layer))
}

p <- ggplot() +
geom_segment(data = links, aes(x = from_layer, xend = to_layer, y = from, yend = to), color = 'grey') +
geom_point(data = data, aes(x = layer, y = node), size = 5, color = 'orange') +
theme_minimal() +
theme(axis.text = element_blank(),
axis.ticks = element_blank(),
panel.grid = element_blank(),
axis.title = element_blank())

if (!is.null(layer_labels)) {
data$layer_label <- layer_labels[data$layer]
p <- p + geom_text_repel(data = data, aes(x = layer, y = max(layers) + 1, label = layer_label), size = 5, nudge_y = 1)
}

if (!is.null(node_labels)) {
data$node_label <- ifelse(data$layer == 1, paste0(node_labels[1], '', data$node),
ifelse(data$layer == length(layers), paste0(node_labels[2], '', data$node), ''))
p <- p + geom_text_repel(data = data, aes(x = layer, y = node, label = node_label), size = 3)
}

return(p)
}

#Example usage
layers <- c(8, 5, 3, 5, 8)
layer_labels <- c('Input Layer', '', 'Latent\nRepresentation', '', 'Output Layer')
neural_network_plot(layers, layer_labels)

```{r}
library(ggplot2)

data <- data.frame(
x = c(1, 2, 2, 3, 4, 4, 1, 2, 3, 4),
y = c(0, 1, -1, 0, 0, 0, 0, 0, 0, 0),
label = c("x_1", "w_1", "w_2", "Σ", "f", "y", "x_2", "w_3", "b", ""),
shape = c("circle", "square", "square", "circle", "square", "square", "circle", "square", "square", "square"),
text_y = c(0.15, 0.15, -0.15, 0, 0.3, 0.3, -0.15, -0.3, 0.15, 0)
)

data$shape <- factor(data$shape, levels = c("circle", "square"))

ggplot(data, aes(x = x, y = y)) +
geom_point(aes(shape = shape), size = 8) +
geom_text(aes(label = label, y = y + text_y), size = 5) +
scale_shape_manual(values = c("circle" = 19, "square" = 15)) +
geom_segment(aes(x = 2, xend = 3, y = 1, yend = 0.2), arrow = arrow(type = "closed", length = unit(0.2, "inches"))) +
geom_segment(aes(x = 2, xend = 3, y = -1, yend = -0.2), arrow = arrow(type = "closed", length = unit(0.2, "inches"))) +
geom_segment(aes(x = 3, xend = 2, y = 0.2, yend = 1), arrow = arrow(type = "closed", length = unit(0.2, "inches"))) +
geom_segment(aes(x = 3, xend = 2, y = -0.2, yend = -1), arrow = arrow(type = "closed", length = unit(0.2, "inches"))) +
geom_segment(aes(x = 3.5, xend = 4.5, y = 0, yend = 0)) +
geom_segment(aes(x = 4.5, xend = 5.5, y = 0, yend = 0)) +
annotate("text", x = 4, y = 0.5, label = "Activation\nFunction", hjust = 0.5) +
annotate("text", x = 5, y = 0, label = "Output", hjust = 0.5) +
annotate("text", x = 3, y = 1.1, label = "Bias\nb", hjust = 0.5) +
geom_rect(aes(xmin = 0.5, xmax = 1.5, ymin = -1.5, ymax = 1.5), color = "black", linetype = "dashed", fill = NA) +
annotate("text", x = 0.3, y = 0, label = "Inputs", angle = 90) +
theme_void() +
xlim(0, 6) +
theme(legend.position = "none")

data <- data.frame(
    x = c(2, 3, 3, 4, 5, 5, 2, 3, 4, 5),
    y = c(0, 1, -1, 0, 0, 0, 0, 0, 0, 0),
    label = c("X", "w_{ji}", "(ai)", "(sum)", "O_j(X)", "m(X)", "X_i", "(e^{-gamma * (X-X[i])^2})", "(e^{-gamma * (Z-Y[j])^2})", "f_j(Z)"),
    shape = c("circle", "square", "circle", "circle", "circle", "circle", "circle", "circle", "circle", "circle"),
    text_y = c(0.15, 0.15, -0.15, 0, 0.3, 0.3, -0.15, -0.3, 0.15, 0)
)

data$shape <- factor(data$shape, levels = c("circle", "square"))

ggplot(data, aes(x = x, y = y)) +
    geom_point(aes(shape = shape), size = 8) +
    geom_text(aes(label = label, y = y + text_y), size = 4) +
    scale_shape_manual(values = c("circle" = 19, "square" = 15)) +
    geom_segment(aes(x = 3, xend = 4, y = 1, yend = 0.2), arrow = arrow(type = "closed", length = unit(0.2, "inches"))) +
    geom_segment(aes(x = 3, xend = 4, y = -1, yend = -0.2), arrow = arrow(type = "closed", length = unit(0.2, "inches"))) +
    geom_segment(aes(x = 4.5, xend = 5.5, y = 0, yend = 0)) +
    annotate("text", x = 5, y = 0.5, label = "Mean Output", hjust = 0.5) +
    annotate("text", x = 4, y = 1.1, label = "Normalized Input\nActivation", hjust = 0.5) +
    annotate("text", x = 4, y = -1.1, label = "Feedback\nActivation", hjust = 0.5) +
    geom_rect(aes(xmin = 1.5, xmax = 2.5, ymin = -1.5, ymax = 1.5), color = "black", linetype = "dashed", fill = NA) +
    annotate("text", x = 1.3, y = 0, label = "Input\nStimulus", angle = 90) +
    annotate("text", x = 3.5, y = -2, label = "Associative Learning Model - Activation and Learning", size = 5, hjust = 0.5) +
    theme_void() +
    xlim(0, 7) +
    theme(legend.position = "none")

data <- data.frame(
    x = c(rep(2, 3), rep(4, 2), rep(6, 3)),
    y = c(-1, 0, 1, 0, 0, -1, 0, 1),
    label = c("e^{-γ(X-X_i)^2}", "Σ", "e^{-γ(Z-Y_j)^2}", "w_{ji}", "a_i(X)", "w_{ji}(t+1)", "O_j(X)", "Y_j"),
    shape = c("circle", "circle", "circle", "square", "square", "circle", "circle", "circle"),
    text_y = c(0.15, 0.15, 0.15, 0, 0, 0.15, 0.15, 0.15)
)

data$shape <- factor(data$shape, levels = c("circle", "square"))

ggplot(data, aes(x = x, y = y)) +
    geom_point(aes(shape = shape), size = 8) +
    geom_text(aes(label = label, y = y + text_y), size = 5) +
    scale_shape_manual(values = c("circle" = 19, "square" = 15)) +
    geom_segment(aes(x = 2, xend = 4, y = 1, yend = 0.2), arrow = arrow(type = "closed", length = unit(0.2, "inches"))) +
    geom_segment(aes(x = 2, xend = 4, y = -1, yend = -0.2), arrow = arrow(type = "closed", length = unit(0.2, "inches"))) +
    geom_segment(aes(x = 4, xend = 6, y = 0, yend = 1), arrow = arrow(type = "closed", length = unit(0.2, "inches"))) +
    geom_segment(aes(x = 4, xend = 6, y = 0, yend = -1), arrow = arrow(type = "closed", length = unit(0.2, "inches"))) +
    annotate("text", x = 3, y = 1.5, label = "Input Layer\nGaussian Activation\na_i(X)=e^{-γ(X-X_i)^2}", hjust = 0.5) +
    annotate("text", x = 5, y = 1.5, label = "Output Layer\nO_j(X)=Σ w_{ji} a_i(X)\nm(X)=Σ Y_j P[Y_j | X]", hjust = 0.5) +
    annotate("text", x = 5, y = -1.5, label = "Learning\nw_{ji}(t+1)=w_{ji}(t)+α{f_j[Z(t)]-O_j[X(t)]}a_i[X(t)]\nf_j(Z)=e^{-γ(Z-Y_j)^2}", hjust = 0.5) +
    theme_void() +
    xlim(0, 8) +
    theme(legend.position = "none")

```{r fig.width=11, fig.height=12}
#| eval: false
# Load the required libraries
library(ggplot2)
library(ggpp)
library(tidyverse)
library(patchwork)

@@

```{r}
#| eval: false 
#| 
# Load the required libraries
library(ggplot2)
library(ggpp)
library(patchwork)
library(tidyverse)

@@

```{r}
#| eval: false
# Load the required packages
library(ggplot2)
library(png)

### 2023-06-12 scratch/rbf.qmd
tikz plots and slight reorganization.

---
title: "rbf.qmd"
format: html
---

```{r}
pacman::p_load(tidyverse,RSNNS)
```

```{r fig.width=11, fig.height=9}

n_iter=500
n_nodes <- c(c(1,3,6,9),seq(10,300,10))
train <- tibble(input=as.matrix(seq(0,100,1)),output=as.matrix(round(2.2*input + 30,0)))

>>>>

---
title: "rbf.qmd"
jupyter: julia-1.9
---

```{r}
pacman::p_load(tidyverse,RSNNS,tikzDevice,knitr)
```

```{r fig.width=11, fig.height=9}
#| eval: false 
n_iter=500
n_nodes <- c(c(1,3,6,9),seq(10,300,10))
train <- tibble(input=as.matrix(seq(0,100,1)),output=as.matrix(round(2.2*input + 30,0)))
